Bullet Groups as a test of $\Lambda$CDM

### 2014-02-28 paper/ms.tex
Update ms.tex

\begin{abstract}
We estimate the expected distribution of displacements between the two
dominand dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that the probability of finding a system
similar with displacements of $\sim$400 kpch$^{-1}$ is between 40\%
for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard model, which
correspond to the observational constraint the object SL2S J08544-0121
that is  a gravitational lens found in the SL2S and located at
z$=0.35$. Given the larger abundance of groups with respect to
clusters, finding multi-modal groups and baryonic-dark matter
displacements.  
\end{abstract}

>>>>

\begin{abstract}
We estimate the expected distribution of displacements between the two
dominant dark matter peaks in halos within a mass range corresponding
to galaxy groups. We find that the probability of finding a system
similar with displacements of $\sim$400 kpch$^{-1}$ is between 40\%
for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard model, which
correspond to the observational constraint the object SL2S J08544-0121
that is  a gravitational lens found in the SL2S and located at
z$=0.35$. Given the larger abundance of groups with respect to
clusters, finding multi-modal groups and baryonic-dark matter
displacements.  
\end{abstract}
